\centering Syscoin 4.0: A Peer-to-Peer Electronic Cash System Built For Business Applications

### 2021-05-14 syscoin_4.0/article.tex
paper corrections

\begin{description}[font=$\bullet$~\normalfont\scshape\color{blue!50!black}]
\item \textbf{Max Coins:} 888 Million
\item \textbf{Deflation:}  5 percent per year until Max Coins
\item \textbf{Consensus:} PoW/PoS Hybrid. PoW is SHA256
Merge-mined with Bitcoin
\item \textbf{Block time:} 60 seconds 
\item \textbf{Rewards:} 38.5 Syscoin deflated 5 percent per year
of which 10 percent is allocated to governance proposals (3.85 Syscoin). 75 percent of the result goes
to masternode and 25 percent to miner.
\item \textbf{Difficulty algorithm:} Dark Gravity Wave
\item \textbf{Masternode collateral requirement:} 100000 Syscoin
\item \textbf{Masternode seniority}: 3 percent every 4 months until
27 percent over 3 years
\item \textbf{Governance proposals payout schedule}: every month
\item \textbf{Governance funding per round}: 168630 Syscoin per
month
\end{description}

\section{Conclusion}
\label{section:conclusion}
Praesent mauris. Fusce nec tellus sed augue semper porta. Mauris massa. Vestibulum lacinia arcu eget nulla. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Curabitur sodales ligula in libero. Sed dignissim lacinia nunc. Curabitur tortor. Pellentesque nibh. Aenean quam. In scelerisque sem at dolor. Maecenas mattis. Sed convallis tristique sem.

>>>>

\begin{description}[font=$\bullet$~\normalfont\scshape\color{blue!50!black}]
\item \textbf{Max Coins:} 888 Million
\item \textbf{Deflation:}  5 percent per year until Max Coins
\item \textbf{Consensus:} PoW/PoS Hybrid. PoW is SHA256
Merge-mined with Bitcoin
\item \textbf{Block time:} 60 seconds 
\item \textbf{Rewards:} 38.5 Syscoin deflated 5 percent per year
of which 10 percent is allocated to governance proposals (3.85 Syscoin). 75 percent of the result goes
to masternode and 25 percent to miner.
\item \textbf{Difficulty algorithm:} Dark Gravity Wave
\item \textbf{Masternode collateral requirement:} 100,000 Syscoin
\item \textbf{Masternode seniority}: 3 percent every 4 months until
27 percent over 3 years
\item \textbf{Governance proposals payout schedule}: every month
\item \textbf{Governance funding per round}: 168,630 Syscoin per
month
\end{description}

\section{Summary}
\label{section:summary}
We have presented what is currently under way for Syscoin 4.0 which will come in the form of a four-layer tech stack to work with the Ethereum ecosystem via our NEVM. With the ever-increasing cost of gas prices, we present the data showing a 1000X+ improvement over Ethereum 2.0 in efficiency in terms of low gas cost per transaction. Syscoin will utilize the best attributes of the top two cryptos, namely Bitcoin and Ethereum. Hence, Syscoin will provide the security offered by Bitcoin while maintaining the programmability of Ethereum. Scalable applications will be mounted on this system via ZKP which will introduce our proposed decentralized cost model on Ethereum gas fees.
